---
title: "P8105 HW5"
author: "Hansheng Zhang"
date: 2021-11-19
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(p8105.datasets)

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
This problem is about homicides in 50 large U.S. cities. The data comes from _The Washington Post_. The solution comes from Jeff's echo recording.

```{r}
homicide_df = 
  read_csv("./Data/homicide-data.csv", na = c("", "uknown")) %>% 
  mutate(city_state = str_c(city, state),
  resolution = case_when(
    disposition == "Closed without arrest" ~ "unsolved",
    disposition == "Open/No arrest"        ~ "unsolved",
    disposition == "Closed by arrest"      ~ "solved"
  )) %>% 
  relocate(city_state)
```

Focusing on Baltimore, MD
```{r, baltimore_df}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")
baltimore_summary =
  baltimore_df %>% 
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
    )
baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n))
baltimore_test %>% 
  broom::tidy() %>% 
  knitr::kable()
```


```{r, prop_test_function}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
      summarise(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
  return(city_test)
  
}
# trying for another city 
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function() %>% 
  broom::tidy() %>% 
  knitr::kable()
```


```{r, iteration}
results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
    ) %>% 
    select(city_state, tidy_results) %>% 
    unnest(tidy_results) %>% 
    select(city_state, estimate, starts_with("conf"))
head(results_df) %>% 
  knitr::kable()
```


```{r}
results_df %>% 
  filter(city_state != "TulsaAL") %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +  
  theme(axis.text.x = element_text(size = 7, angle = 90, vjust = 0.5, hjust = 1))
  
``` 

## Problem 2

```{r}
data_path = str_c("./Data/", list.files(path = "./Data/"))
new_data = tibble(
  file_name = list.files(path = "./Data/"),
  participants = purrr::map(data_path, read_csv) 
) %>% 
  separate(file_name, into = c("arm","ID"), sep = "_") %>% 
  separate(col = "ID", into = c("id", "csv")) %>%
  mutate(
    arm = recode(arm, con = "control", exp = "experiment" )
    ) %>% 
  select(-csv) %>% 
  unnest(participants) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate(week = as.numeric(week)) %>%
  mutate(arm = as.factor(arm))
  
new_data
  
```

Making a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
new_data %>% 
 ggplot(aes(x = week, y = observations, color = id)) +
  facet_grid(. ~ arm) +
  geom_line() +
   labs(
    title = "Comparison of Observarion Values Between Groups",
    x = "Time (weeks)",
    y = "Results"
    )
```

Subjects in the experimental group appear to increase in value over weeks 1-8, while no trends were observed in subjects in the control group. The results of the experimental group also appear to be higher than the control group.  


## Problem 3
Load 'iris' dataset
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. 
```{r, error = FALSE}
missing_value = function(x) {
   if (is.numeric(x)) {
     replace_na(x, round(mean(x,na.rm = TRUE), digits = 1))
   }
   else if(is.character(x)){
    replace_na(x,"virginica")
   }
} 
map_dfr(iris_with_missing, missing_value)
```
